# Ontario

## Research questions

```{r label = "global-options", include=FALSE}

### setting up working environment
### for details see: https://yihui.name/knitr/options/
knitr::opts_chunk$set(
        collapse = T,
        echo = F,
        message = T,
        error = T,
        warning = T,
        comment = '##',
        highlight = T,
        prompt = F,
        strip.white = T,
        tidy = T
        )

### installing and loading packages
### https://www.tidyverse.org/
if (!require("tidyverse"))
        {install.packages("tidyverse", repos = 'http://cran.wu.ac.at/')
        library(tidyverse)}

### above command installed and loaded the core tidyverse packages:
# ggplot2: data visualization
# tibble:  a modern take on data frames
# tidyr:   data tidying
# readr:   data import (csv, tsv, fwf)
# purrr:   functional R programming
# dplyr:   data (frame) manipulation
# stringr: string manipulation
# forcats: working with categorical variables

# I am going to use the `janitor` package for calculating table totals
if (!require("janitor"))
        {install.packages("janitor", repos = 'http://cran.wu.ac.at/')
        library(janitor)}

if (!require("reshape2"))
        {install.packages("reshape2", repos = 'http://cran.wu.ac.at/')
        library(reshape2)}

### generate my theme
my_theme <- theme_light() +
        theme(plot.title = element_text(size = 10, face = "bold", hjust = 0.5)) +
        theme(plot.background = element_rect(color = NA, fill = NA)) +
        theme(plot.margin = margin(1, 0, 0, 0, unit = 'cm'))

```

## Overall distribution of H5P content types


```{r ct-all, fig.height = 7, fig.width=7}
library(readODS)
CT_all <- read_ods(
    path = "ontario_data/H5P-Content-Types-2020-10-13.ods",
    sheet = 1
    )
CT_all[is.na(CT_all)] <- 0 # replace NA with 0
colnames(CT_all) <- c("Content Type", "n")

CT_all$row_num <- seq.int(nrow(CT_all))

# plot1 <- ggplot(CT_all, aes(x=reorder(`Content Type`,-row_num), y=n)) + 
#     geom_bar(stat="identity") +
#     coord_flip() +
#     my_theme +
#     ggtitle("Distribution of H5P Content Types at the Ontario Repository (sorted alphabetically")
# plot1

plot2 <- ggplot(CT_all, aes(x=reorder(`Content Type`,n), y=n)) + 
    geom_bar(stat="identity") +
    coord_flip() +
    my_theme +
    xlab("Name of H5P Content Types") +
    ylab("Number of Content Types") +
    ggtitle("Distribution of H5P Stand-alone Content Types 
            in the Ontario Repository (2020-10-13)") +
    geom_text(aes(label=n), size=2.8, hjust=-0.2)
plot2


```
## Distribution by discipline

```{r ct-subject}

CT_subject <- read_ods(
    path = "ontario_data/H5P-Content-Types-2020-10-13.ods",
    sheet = 2
    )
CT_subject[is.na(CT_subject)] <- 0 # replace NA with 0

CT_subject_sums <- adorn_totals(CT_subject, where = "row", fill = "-", na.rm = TRUE, name = "Total")

Count_per_subject <- CT_subject_sums[nrow(CT_subject_sums) ,]
Count_per_subject <-  melt(Count_per_subject, variable.name="Discipline", value.name="N")
Count_per_subject <- Count_per_subject[, -1]

disciplines = c("Business & Management", "The Arts", "Computing & IT", "Law", "Earth & Environment", "Health & Development", "History", "Language & Linguistics", "Literature", "Mathematics & Science", "Medicine & Nursing", "Philosophy & Religion", "Reference", "Society & Social Sciences", "Technology & Engineering")

Count_per_subject$Discipline = disciplines

# png(filename="count_per_subject1.png", width=600, height=500)
plot3 <- ggplot(Count_per_subject, aes(x=reorder(Discipline, N), y = N)) +
    geom_bar(stat="identity") +
    coord_flip() +
    my_theme +
    xlab("Discipline") +
    ylab("Number of Content Types in the Ontario Repository") +
    ggtitle("Usage of H5P Content Types by Discipline at the Ontario Repository") +
    geom_text(aes(label=N), size=3, hjust=-0.2)
plot3
# dev.off()


```

## Distribution in Question Sets

```{r ct-question-set, fig.height = 4, fig.width=7}

sheetName <- list_ods_sheets("ontario_data/Questions-Set-2020-10-14.ods")
i <- length(sheetName)
for(i in 1:i){
    assign(paste0("CT_QS_", sheetName[i]), {
        read_ods(
            path = "ontario_data/Questions-Set-2020-10-14.ods",
            sheet = i)
        }
    )
}

id_vec <- CT_QS_Business$ID

CT_QS_df <- data.frame(cbind(id_vec,
           CT_QS_Business$Total,
           CT_QS_Arts$Total,
           CT_QS_IT$Total,
           CT_QS_Law$Total,
           CT_QS_Earth$Total,
           CT_QS_Health$Total,
           CT_QS_History$Total,
           CT_QS_Language$Total,
           CT_QS_Literature$Total,
           CT_QS_Math$Total,
           CT_QS_Medicine$Total,
           CT_QS_Philosophy$Total,
           CT_QS_Reference$Total,
           CT_QS_Society$Total,
           CT_QS_Technology$Total
           ))

CT_QS_df[is.na(CT_QS_df)] <- 0 # replace NA with 0
colnames(CT_QS_df) <- c("ContentType", sheetName)

CT_QS_df_long <- melt(CT_QS_df, 
                      id.vars = "ContentType",
                      variable.name = "Discipline",
                      value.name = "n")
CT_QS_df_long$n <- as.integer(CT_QS_df_long$n)


plot4 <- ggplot(CT_QS_df_long, aes(x=ContentType, y=n, fill=Discipline)) +
    geom_bar(stat="identity") +
    # coord_flip() +
    # guides(fill=guide_legend(reverse=TRUE))
    my_theme +
    xlab("H5P Content Types used within Question Set") +
    ylab("Number of Content Types used within Question Sets") +
    ggtitle("Usage of H5P Content Types within Question Sets by Disciplines at the Ontario Repository") +
    theme(axis.text.x = element_text(angle=50,hjust=1 ))
    
plot4

plot5 <- ggplot(CT_QS_df_long, 
                aes(x=Discipline, y=n, fill=ContentType)) +
    geom_bar(stat="identity") +
    # coord_flip() +
    # guides(fill=guide_legend(reverse=TRUE))
    my_theme +
    xlab("H5P Content Types used within Question Sets by Discipline") +
    ylab("Number of Content Types used within Question Sets") +
    ggtitle("Usage of H5P Content Types within Question Sets by Discipline at the Ontario Repository") +
    theme(axis.text.x = element_text(angle=50,hjust=1 ))
plot5


```

## Distribution in Course Presentations


```{r ct-course-presentation, fig.height = 4, fig.width=7}

sheetName <- list_ods_sheets("ontario_data/Course-Presentation-2020-10-15.ods")
i <- length(sheetName)
for(i in 1:i){
    assign(paste0("CT_CP_", sheetName[i]), {
        read_ods(
            path = "ontario_data/Course-Presentation-2020-10-15.ods",
            sheet = i)
        }
    )
}

id_vec <- CT_CP_Business$ID

CT_CP_df <- data.frame(cbind(id_vec,
           CT_CP_Business$Total,
           CT_CP_Arts$Total,
           CT_CP_IT$Total,
           CT_CP_Law$Total,
           CT_CP_Earth$Total,
           CT_CP_Health$Total,
           CT_CP_History$Total,
           CT_CP_Language$Total,
           CT_CP_Literature$Total,
           CT_CP_Math$Total,
           CT_CP_Medicine$Total,
           CT_CP_Philosophy$Total,
           CT_CP_Reference$Total,
           CT_CP_Society$Total,
           CT_CP_Technology$Total
           ))

CT_CP_df[is.na(CT_CP_df)] <- 0 # replace NA with 0
colnames(CT_CP_df) <- c("ContentType", sheetName)

CT_CP_df_long <- melt(CT_CP_df, 
                      id.vars = "ContentType",
                      variable.name = "Discipline",
                      value.name = "n")
CT_CP_df_long$n <- as.integer(CT_CP_df_long$n)


plot6 <- ggplot(CT_CP_df_long, aes(x=ContentType, y=n, fill=Discipline)) +
    geom_bar(stat="identity") +
    # coord_flip() +
    # guides(fill=guide_legend(reverse=TRUE))
    my_theme +
    xlab("H5P Content Types used within Course Presentation") +
    ylab("Number of Content Types used within Course Presentation") +
    ggtitle("Usage of H5P Content Types in Course Presentation by Disciplines at the Ontario Repository") +
    theme(axis.text.x = element_text(angle=50,hjust=1 ))
    
plot6

plot7 <- ggplot(CT_CP_df_long, 
                aes(x=Discipline, y=n, fill=ContentType)) +
    geom_bar(stat="identity") +
    # coord_flip() +
    # guides(fill=guide_legend(reverse=TRUE))
    my_theme +
    xlab("H5P Content Types used within Course Presentation by Discipline") +
    ylab("Number of Content Types used within Course Presentations") +
    ggtitle("Usage of H5P Content Types within Course Presentation by Discipline at the Ontario Repository") +
    theme(axis.text.x = element_text(angle=50,hjust=1 ))
plot7


```
## Distribution in Interactive Video

```{r ct-interactive-video, fig.height = 4, fig.width=7}

sheetName <- list_ods_sheets("ontario_data/Interactive-Video-2020-10-16.ods")
i <- length(sheetName)
for(i in 1:i){
    assign(paste0("CT_IV_", sheetName[i]), {
        read_ods(
            path = "ontario_data/Interactive-Video-2020-10-16.ods",
            sheet = i)
        }
    )
}

id_vec <- CT_IV_Business$ID

CT_IV_df <- data.frame(cbind(id_vec,
           CT_IV_Business$Total,
           CT_IV_Arts$Total,
           CT_IV_IT$Total,
           CT_IV_Law$Total,
           CT_IV_Earth$Total,
           CT_IV_Health$Total,
           CT_IV_History$Total,
           CT_IV_Language$Total,
           CT_IV_Literature$Total,
           CT_IV_Math$Total,
           CT_IV_Medicine$Total,
           CT_IV_Philosophy$Total,
           CT_IV_Reference$Total,
           CT_IV_Society$Total,
           CT_IV_Technology$Total
           ))
CT_IV_df[is.na(CT_IV_df)] <- 0 # replace NA with 0
colnames(CT_IV_df) <- c("ContentType", sheetName)

CT_IV_df_long <- melt(CT_IV_df, 
                      id.vars = "ContentType",
                      variable.name = "Discipline",
                      value.name = "n")
CT_IV_df_long$n <- as.integer(CT_IV_df_long$n)


plot8 <- ggplot(CT_IV_df_long, aes(x=ContentType, y=n, fill=Discipline)) +
    geom_bar(stat="identity") +
    # coord_flip() +
    # guides(fill=guide_legend(reverse=TRUE))
    my_theme +
    xlab("H5P Content Types used within Interactive Video") +
    ylab("Number of Content Types used within Interactive Videon") +
    ggtitle("Usage of H5P Content Types in Interactive Video by Disciplines at the Ontario Repository") +
    theme(axis.text.x = element_text(angle=50,hjust=1 ))
    
plot8

plot9 <- ggplot(CT_IV_df_long, 
                aes(x=Discipline, y=n, fill=ContentType)) +
    geom_bar(stat="identity") +
    # coord_flip() +
    # guides(fill=guide_legend(reverse=TRUE))
    my_theme +
    xlab("H5P Content Types used within Interactive Video by Discipline") +
    ylab("Number of Content Types used within Interactive Video") +
    ggtitle("Usage of H5P Content Types within Interactive Video by Discipline at the Ontario Repository") +
    theme(axis.text.x = element_text(angle=50,hjust=1 ))
plot9


```

## Converting strings to numeric data

```{r convert-chr-to-num}

i <- c(2:16)                                  # Specify columns you want to change

CT_QS_df[ , i] <- apply(CT_QS_df[ , i], 2,    # Specify own function within apply
                    function(x) as.numeric(x))  
CT_CP_df[ , i] <- apply(CT_CP_df[ , i], 2,    # Specify own function within apply
                    function(x) as.numeric(x))
CT_IV_df[ , i] <- apply(CT_IV_df[ , i], 2,    # Specify own function within apply
                    function(x) as.numeric(x))
```



## Summarising compound content types

```{r db_totals}

CT_QS_sums <- adorn_totals(CT_QS_df, where = c("row","col"), fill = "-", na.rm = TRUE, name = "Total")
CT_CP_sums <- adorn_totals(CT_CP_df, where = c("row","col"), fill = "-", na.rm = TRUE, name = "Total")
CT_IV_sums <- adorn_totals(CT_IV_df, where = c("row","col"), fill = "-", na.rm = TRUE, name = "Total")
```

## Add values from compound content types to CT_all 


```{r total-ct-with-compounds}

### add column to CT_all
CT_all["Compounds"] <-  0L 

### create df with only rows of Name and Total (easier to check)
CP_sums <- CT_CP_sums[, c(1,17)]
IV_sums <- CT_IV_sums[, c(1,17)]
QS_sums <- CT_QS_sums[, c(1,17)]


######### start with the calculation and transfer of the values

### Dialog Cards (CP)
CT_all[11,4] <-  CP_sums[2,2]


### Drag and Drop (QS, CP, IV)
compound_drag_drop <- bind_rows( filter(CT_QS_df, ContentType == "Drag and Drop"),
                        filter(CT_CP_df, ContentType == "Drag and Drop"),
                        filter(CT_IV_df, ContentType == "Drag and Drop"))
compound_drag_drop <- adorn_totals(compound_drag_drop, where = c("row","col"), 
                                   fill = "-", na.rm = TRUE, name = "Total")
CT_all[14,4] <-  compound_drag_drop[4,17]

### Drag Text (all 3)
compound_drag_text <- bind_rows(filter(CT_QS_df, ContentType == "Drag Text"),
          filter(CT_CP_df, ContentType == "Drag Text"),
          filter(CT_IV_df, ContentType == "Drag Text"))
compound_drag_text <- adorn_totals(compound_drag_text, where = c("row","col"), 
                                   fill = "-", na.rm = TRUE, name = "Total")
CT_all[15,4] <-  compound_drag_text[4,17]


### Essay (IV, QS)
compound_essay <- bind_rows(filter(CT_QS_df, ContentType == "Essay"),
          filter(CT_IV_df, ContentType == "Essay"))
compound_essay <- adorn_totals(compound_essay, where = c("row","col"), 
                               fill = "-", na.rm = TRUE, name = "Total")
CT_all[16,4] <-  compound_essay[3,17]

### Fill in the Blanks (all 3)
compound_fill_blanks <- bind_rows(filter(CT_QS_df, ContentType == "Fill in the Blanks"),
          filter(CT_CP_df, ContentType == "Fill in the Blanks"),
          filter(CT_IV_df, ContentType == "Fill in the Blanks"))
compound_fill_blanks <- adorn_totals(compound_fill_blanks, where = c("row","col"), 
                               fill = "-", na.rm = TRUE, name = "Total")
CT_all[17,4] <-  compound_fill_blanks[4,17]

### Image Hotspots (IV)
CT_all[24,4] <-  IV_sums[5,2]

### Interactive Video (CP)
CT_all[31,4] <-  CP_sums[7,2]

### Mark the Words (all 3)
compound_mark_words <- bind_rows(filter(CT_QS_df, ContentType == "Mark the Words"),
          filter(CT_CP_df, ContentType == "Mark the Words"),
          filter(CT_IV_df, ContentType == "Mark the Words"))
compound_mark_words <- adorn_totals(compound_mark_words, where = c("row","col"), 
                               fill = "-", na.rm = TRUE, name = "Total")
CT_all[33,4] <-  compound_mark_words[4,17]

### Multiple Choice (all 3)
compound_multiple_choice <- bind_rows(filter(CT_QS_df, ContentType == "Multiple Choice"),
          filter(CT_CP_df, ContentType == "Multiple Choice"),
          filter(CT_IV_df, ContentType == "Multiple Choice"))
compound_multiple_choice <- adorn_totals(compound_multiple_choice, where = c("row","col"), 
                               fill = "-", na.rm = TRUE, name = "Total")
CT_all[35,4] <-  compound_multiple_choice[4,17]

### Questionnaire (IV)
CT_all[37,4] <- IV_sums[8,2]

### Single Choice Set (CP, IV)
compound_single_choice <- bind_rows(filter(CT_CP_df, ContentType == "Single Choice Set"),
          filter(CT_IV_df, ContentType == "Single Choice Set"))
compound_single_choice <- adorn_totals(compound_single_choice, where = c("row","col"), 
                               fill = "-", na.rm = TRUE, name = "Total")
CT_all[39,4] <-  compound_single_choice[3,17]

### Summary (CP, IV)
compound_summary <- bind_rows(filter(CT_CP_df, ContentType == "Summary"),
          filter(CT_IV_df, ContentType == "Summary"))
compound_summary <- adorn_totals(compound_summary, where = c("row","col"), 
                               fill = "-", na.rm = TRUE, name = "Total")
CT_all[42,4] <-  compound_summary[3,17]

### True/False Question (all 3)
compound_true_false <- bind_rows(filter(CT_QS_df, ContentType == "True/False Question"),
          filter(CT_CP_df, ContentType == "True/False Question"),
          filter(CT_IV_df, ContentType == "True/False Question"))
compound_true_false <- adorn_totals(compound_true_false, where = c("row","col"), 
                               fill = "-", na.rm = TRUE, name = "Total")
CT_all[44,4] <-  compound_true_false[4,17]


### Calculate new total
CT_all <- CT_all %>% 
    select(-row_num) %>% 
    mutate(Total = n + Compounds)


```

```{r ct_all_compounds, fig.height = 7, fig.width=7}
plot10 <- ggplot(CT_all, aes(x=reorder(`Content Type`,Total), y=Total)) + 
    geom_bar(stat="identity") +
    coord_flip() +
    my_theme +
    xlab("Name of H5P Content Types") +
    ylab("Number of all Content Types (Stand-alone and Compound)") +
    ggtitle("Distribution of all H5P Content Types (Stand-alone and Compound)
            in the Ontario Repository (2020-10-13)") +
    geom_text(aes(label=Total), size=2.8, hjust=-0.2)
plot10
```

## Discipline all

```{r ct-disciplines-all}

CT_subject_compounds <- bind_rows(CT_QS_df, CT_CP_df, CT_IV_df)
CT_subject_stand_alone <- rename(CT_subject, ContentType = Name)
CT_subject_all <- bind_rows(CT_subject_stand_alone, CT_QS_df, CT_CP_df, CT_IV_df)
CT_subject_all_sums <- adorn_totals(CT_subject_all, where = c("row","col"), fill = "-", na.rm = TRUE, name = "Total")

```


## Some preliminiary data for a blog entry

```{r blog-data}
sum(CT_all$n)
sum(CT_all$Total)
```

