# Ontario

## Research questions

```{r label = "global-options", include=FALSE}

### setting up working environment
### for details see: https://yihui.name/knitr/options/
knitr::opts_chunk$set(
        collapse = T,
        echo = F,
        message = T,
        error = T,
        warning = T,
        comment = '##',
        highlight = T,
        prompt = F,
        strip.white = T,
        tidy = T
        )

### installing and loading packages

# If you need functions from both plyr and dplyr, please load plyr first, then dplyr:
if (!require("plyr"))
        {install.packages("plyr", repos = 'http://cran.wu.ac.at/')
        library(plyr)}

### https://www.tidyverse.org/
if (!require("tidyverse"))
        {install.packages("tidyverse", repos = 'http://cran.wu.ac.at/')
        library(tidyverse)}

### above command installed and loaded the core tidyverse packages:
# ggplot2: data visualization
# tibble:  a modern take on data frames
# tidyr:   data tidying
# readr:   data import (csv, tsv, fwf)
# purrr:   functional R programming
# dplyr:   data (frame) manipulation
# stringr: string manipulation
# forcats: working with categorical variables

# I am going to use the `janitor` package for calculating table totals
if (!require("janitor"))
        {install.packages("janitor", repos = 'http://cran.wu.ac.at/')
        library(janitor)}

if (!require("reshape2"))
        {install.packages("reshape2", repos = 'http://cran.wu.ac.at/')
        library(reshape2)}

if (!require("readODS"))
        {install.packages("readODS", repos = 'http://cran.wu.ac.at/')
        library(readODS)}

### generate my theme
my_theme <- theme_light() +
        theme(plot.title = element_text(size = 10, face = "bold", hjust = 0.5)) +
        theme(plot.background = element_rect(color = NA, fill = NA)) +
        theme(plot.margin = margin(1, 0, 0, 0, unit = 'cm'))

### global variables

vec.subject.short = c("Business", "Arts", "IT", "Law", "Earth", "Health", "History", "Language", "Literature", "Math", "Medicine", "Philosophy", "Reference", "Society", "Technology")

vec.subject.long = c("Business & Management", "The Arts", "Computing & IT", "Law", "Earth & Environment", "Health & Development", "History", "Language & Linguistics", "Literature", "Mathematics & Science", "Medicine & Nursing", "Philosophy & Religion", "Reference", "Society & Social Sciences", "Technology & Engineering")

vec.question.set = c("Drag and Drop", "Drag Text", "Essay", "Fill in the Blanks", "Mark the Words",
                 "Multiple Choice", "True/False Question")
vec.course.presentation =  c("Dialog Cards", "Drag and Drop", "Drag Text", "Fill in the Blanks",
                         "Interactive Video", "Mark the Words", "Multiple Choice", "Single Choice Set",
                         "Summary", "True/False Question")
vec.interactive.video =  c("Drag and Drop", "Drag Text", "Essay", "Fill in the Blanks", "Image
                           Hotspots", "Mark the Words", "Multiple Choice", "Questionnaire", 
                           "Single Choice Set","Summary", "True/False Question")
vec.compounds =  c("Dialog Cards", "Drag and Drop", "Drag Text", "Essay", "Fill in the Blanks", 
                   "Interactive Video", "Image Hotspots", "Mark the Words", "Multiple Choice", 
                   "Questionnaire", "Single Choice Set", "Summary", "True/False Question")
vec.compound.names = c("Question Set", "Course Presentation", "Interactive Video")

vec.lotCT.disciplines = c("ContentType", "Business", "IT", "Language", "Math", 
                          "Medicine", "Reference", "Society", "Technology")

QS.group.colours =  c(
                   "Drag and Drop" = "#E68601", 
                   "Drag Text" = "#F967A3", 
                   "Essay" =  "black", #"#E76BF3", 
                   "Fill in the Blanks" = "#6BB100", 
                   "Mark the Words" = "#619CFF", 
                   "Multiple Choice" = "#F961D2", 
                   "True/False Question" = "#2FBFC4")

CP.group.colours =  c("Dialog Cards" = "#F7756D",
                   "Drag and Drop" = "#E68601", 
                   "Drag Text" = "#F967A3", 
                   "Fill in the Blanks" = "#6BB100", 
                   "Interactive Video" = "grey", #"#24B0F5",
                   "Mark the Words" = "#619CFF", 
                   "Multiple Choice" = "#F961D2", 
                   "Single Choice Set" = "darkblue", #"#F961D2",
                   "Summary" = "#C99801",
                   "True/False Question" = "#2FBFC4")

IV.group.colours =  c(
                   "Drag and Drop" = "#E68601", 
                   "Drag Text" = "#F967A3", 
                   "Essay" = "black", #"#E76BF3", 
                   "Fill in the Blanks" = "#6BB100", 
                   "Image Hotspots" = "#31C0AF", 
                   "Mark the Words" = "#619CFF", 
                   "Multiple Choice" = "#F961D2",
                   "Questionnaire" = "#A2A500",
                   "Single Choice Set" = "darkblue", #"#F961D2",
                   "Summary" = "#C99801", 
                   "True/False Question" = "#2FBFC4")
```

## Stand-alone distribution of H5P content types


```{r stand-alone}

#########    read data for overall content types   ###############
library(readODS)
df.sa.type <- read_ods(
    path = "ontario_data/H5P-Content-Types-2020-10-13.ods",
    sheet = 2,
    )


#########     read data for content types by discipline ##########
df.sa.subject <- read_ods(
    path = "ontario_data/H5P-Content-Types-2020-10-13.ods",
    sheet = 3,
    )


df.sa.subject.sum <-  df.sa.subject %>%
    adorn_totals("row") %>% 
    filter(ContentType == "Total") %>% 
    select(all_of(vec.subject.short)) %>% 
    gather(all_of(vec.subject.short), key = "Discipline", value = "Total") %>% 
    mutate(Discipline = vec.subject.long)



#########      READ DATA FOR COMPOUND CONTENT TYPES          ################



#################        QUESTION SET            ########################

# see: https://stackoverflow.com/questions/17499013/how-do-i-make-a-list-of-data-frames
LL.Question.Sets =  list()
sheetNames <- list_ods_sheets("ontario_data/Question-Set-2020-10-14.ods")
i <- length(sheetNames)
for(i in 2:i){                             # i start with 2 because first sheet = Intro
    LL.Question.Sets[[i-1]] <-                 # but list starts with 1
        read_ods(             
                path = "ontario_data/Question-Set-2020-10-14.ods",
                sheet = i
                )
}
### see: https://stackoverflow.com/questions/20987295/rename-multiple-columns-by-names
names(LL.Question.Sets) <- vec.subject.short

#################        COURSE PRESENTATION        ########################

LL.Course.Presentations =  list()
sheetNames <- list_ods_sheets("ontario_data/Course-Presentation-2020-10-15.ods")
i <- length(sheetNames)
for(i in 2:i){                          
    LL.Course.Presentations[[i-1]] <-  read_ods(             
                path = "ontario_data/Course-Presentation-2020-10-15.ods",
                sheet = i
                )
}
names(LL.Course.Presentations) <- vec.subject.short

##################        INTERACTIVE VIDEO        ########################

LL.Interactive.Videos =  list()
sheetNames <- list_ods_sheets("ontario_data/Interactive-Video-2020-10-16.ods")
i <- length(sheetNames)
for(i in 2:i){                             
    LL.Interactive.Videos[[i-1]] <-read_ods(             
                path = "ontario_data/Interactive-Video-2020-10-16.ods",
                sheet = i
                )
}

names(LL.Interactive.Videos) <- vec.subject.short

##################        MULTIPLE CONTENT TYPES        ########################

### some CTs are counted multiple times when ordered by subject
LL.Multiple.Values =  list()
sheetNames <- list_ods_sheets("ontario_data/Content-Types-multiple.ods")
i <- length(sheetNames)
for(i in 2:i){                             
    LL.Multiple.Values[[i-1]] <-read_ods(             
                path = "ontario_data/Content-Types-multiple.ods",
                sheet = i
                )
}

names(LL.Multiple.Values) <- vec.compound.names


```



```{r test1, eval=FALSE, fig.height=2, fig.width=5}
library(tidyverse)

df = tribble(
  ~Type, ~N,
  "A", 72,
  "B", 14,
  "C", 25,
  "D",  9
)

ggplot(df, aes(x=Type, y=N)) +
  geom_bar(stat="identity") +
  coord_flip() +
  scale_x_discrete(expand = expansion(mult = c(0, 0))) +
  scale_y_continuous(expand = expansion(mult = c(0, .05)))
  

ggplot(mtcars) +
  geom_bar(aes(x = factor(cyl))) +
  coord_flip() +
  scale_y_continuous(expand = expansion(mult = c(0, 0))) +
  scale_x_discrete(expand = expansion(mult = c(0, 0)))


# scale_y_discrete(expand = expansion(mult = c(0, .05)), limits=c(0, 20,40, 60))
```



## Distribution in Course Presentations

```{r prepare-plot}

######      bind all total cols   ######################
df.QS.total =  as_tibble(bind_cols(LL.Question.Sets))
df.QS.total = select(df.QS.total, c(1,starts_with("Total")))
names(df.QS.total) <- c("ContentType", vec.subject.short)

df.CP.total =  as_tibble(bind_cols(LL.Course.Presentations))
df.CP.total = select(df.CP.total, c(1,starts_with("Total")))
names(df.CP.total) <- c("ContentType", vec.subject.short)

df.IV.total =  as_tibble(bind_cols(LL.Interactive.Videos))
df.IV.total = select(df.IV.total, c(1,starts_with("Total")))
names(df.IV.total) <- c("ContentType", vec.subject.short)

##############  reshape data from wide to long  #############


df.QS.long <- melt(df.QS.total, 
                      id.vars = "ContentType",
                      variable.name = "Discipline",
                      value.name = "n")

df.CP.long <- melt(df.CP.total, 
                      id.vars = "ContentType",
                      variable.name = "Discipline",
                      value.name = "n")

df.IV.long <- melt(df.IV.total, 
                      id.vars = "ContentType",
                      variable.name = "Discipline",
                      value.name = "n")

df.sa.subject.long <- melt(df.sa.subject, 
                      id.vars = "ContentType",
                      variable.name = "Discipline",
                      value.name = "n")

df.QSlot.long <- df.QS.total %>% 
    select(vec.lotCT.disciplines) %>%
    melt(id.vars = "ContentType",
        variable.name = "Discipline",
        value.name = "n")


```
## Add compounds

```{r add-compounds-data}

### prepare df for union: 
df.QS.col.total <-  adorn_totals(df.QS.total, "col")
df.CP.col.total <-  adorn_totals(df.CP.total, "col")
df.IV.col.total <-  adorn_totals(df.IV.total, "col")

df.compounds <- 
    tibble(ContentType = vec.compounds) %>% 
    full_join(df.QS.col.total[, c(1,17)], by = "ContentType") %>% 
    full_join(df.CP.col.total[, c(1,17)], by = "ContentType") %>% 
    full_join(df.IV.col.total[, c(1,17)], by = "ContentType") %>% 
    adorn_totals("col", name = "Overall")

df.overall <-  
    full_join(df.sa.type, df.compounds[, c(1,5)], by = "ContentType") %>% 
    full_join(LL.Multiple.Values$`Interactive Video`[, c(1, 
                         ncol(LL.Multiple.Values$`Interactive Video`))],
                         by = "ContentType") %>% 
    replace_na(list(Overall.y = 0, Total = 0)) %>% 
    mutate(Overall = Overall.y - Total) %>% 
    select(c(-Overall.y, -Total)) %>% 
    rename("Stand.Alone" = Overall.x, "Compounds" = Overall) %>% 
    adorn_totals("col") 

df.overall.sum <- df.overall %>% 
  adorn_totals("row") %>% 
  filter(ContentType == "Total")

df.overall.long <- gather(df.overall,
                          `Stand.Alone`, `Compounds`, key = "CT", value = N)

###############################################################################
##### compound by discipline

df.QS.disc.total <-  df.QS.total %>% 
  adorn_totals("row", name = "QS.Total") %>% 
  filter(ContentType == "QS.Total")

df.CP.disc.total <-  df.CP.total %>% 
  adorn_totals("row", name = "CP.Total") %>% 
  filter(ContentType == "CP.Total")

df.IV.disc.total <-  df.IV.total %>% 
  adorn_totals("row", name = "IV.Total") %>% 
  filter(ContentType == "IV.Total")

df.disc <- bind_rows(df.QS.disc.total, df.CP.disc.total, df.IV.disc.total ) %>% 
  pivot_longer(!ContentType, names_to = "Discipline", values_to = "N") %>% 
  pivot_wider(names_from = ContentType, values_from = N) %>% 
  bind_cols("SA.Total" = df.sa.subject.sum[,2]) %>% 
  relocate(SA.Total, QS.Total, IV.Total, CP.Total,  .after = "Discipline")



# compare CTs in different environment: SA, QS, CP, IV
# only with disciplines which have more than 30 SA CTs
 df.disc.30.long <-  df.disc %>% 
  mutate(Discipline = vec.subject.long) %>% 
  filter(SA.Total > 30) %>% 
  adorn_totals("col", name = "Overall") %>% 
  pivot_longer(cols = 2:5, names_to = "CT.Kind", values_to = "N") %>% 
  group_by(Discipline) %>% 
  mutate(label_y = cumsum(N) - 0.5 * N)
  


```


## Display and save plots

### Content types per count

#### Stand-alone content types with sums, ordered by count

```{r CT-stand-alone-sum, fig.height=10, fig.width=8}
ggplot(df.sa.type, aes(x=reorder(`ContentType`, Overall), y=Overall)) + 
    geom_bar(stat="identity", width = .7, fill= "#2fbfc4", colour = "#2fbfc4") +
    coord_flip() +
    my_theme +
    xlab("Name of H5P Content Types") +
    ylab("Number of Content Types") +
    ggtitle("Distribution of H5P Stand-alone Content Types in the Ontario Repository (2020-10-13)") +
    geom_text(aes(label=Overall), size=2.5, hjust=-0.2) +
    theme(plot.margin = margin(12,12,12,12)) +
    scale_x_discrete(expand = expansion(mult = c(0, 0))) +
    scale_y_continuous(expand = expansion(mult = c(0, .05)))


ggsave("ontario-plots/CT-stand-alone-sum.pdf",
    width = 8,
    height = 10
    )

```

#### All content types with sums, ordered by count of stand-alones 

```{r CT-all-sum-sa-order, fig.height=10, fig.width=8}
df.overall.old.order <- bind_cols(df.overall, Overall = df.sa.type$Overall)
ggplot(df.overall.old.order, aes(x=reorder(ContentType, Overall), y = Total)) +
    geom_bar(stat="identity", width = .8, fill= "#2fbfc4", colour = "#2fbfc4") +
    coord_flip() +
    my_theme +
    xlab("Content Types") +
    ylab("Number of Content Types in the Ontario Repository") +
    ggtitle("H5P Content Types (Stand-alone and Compounds) in the Ontario Repository,
            ordered by the number of Stand-alone Content Types") +
    geom_text(aes(label=Total), size=2.5, hjust=-0.5) +
    theme(plot.margin = margin(12,12,12,12)) +
    scale_x_discrete(expand = expansion(mult = c(0, 0))) +
    scale_y_continuous(expand = expansion(mult = c(0, .05)))

ggsave(
    filename = "ontario-plots/CT-all-sum-sa-order.pdf",
    width = 8,
    height = 10
    )

```

#### Stand-alone and compounds content types with sums, ordered by count

```{r CT-sa-compound-sums, fig.height=10, fig.width=8}

my2.fun <- function(trait, n, cum) {
  for(i in 1:length(trait)){
    if(trait[i] == "Stand.Alone") {
      n[i] <- -5
    }

    if(trait[i] == "Compounds") {
      s <- paste0(n[i], cum[i])
      if(nchar(s) >= 6){n[i] <-cum[i] +70}
      if(nchar(s) == 5){n[i] <-cum[i] +65}
      if(nchar(s) == 4){n[i] <-cum[i] +60}
      if(nchar(s) == 3){n[i] <-cum[i] +50}
      if(nchar(s) == 2){n[i] <-cum[i] +40}
    }
  }
  return (n)
}

df.final <- df.overall.long %>% 
  mutate(label_y = my2.fun(CT, N, Total)) %>% 
  mutate(Overall = ifelse(CT == "Compounds", paste0(N, "/", Total), as.character(N)))

ggplot(df.final, aes(x=reorder(ContentType, Total), y=N, fill=CT)) +
  geom_bar(stat="identity", width = .8) +
  coord_flip() + 
  my_theme +
  labs(x = "Content Type", 
       y = "Number of Content Types in the Ontario Repository",
       title = "Content Types (Stand-Alone and Compounds) in the Ontario Repository",
       fill = "Content Types"
       ) +
  geom_text(aes(y=label_y, label=Overall), size=2.5, hjust = 1) +
  theme(plot.margin = margin(12,12,12,12),
        legend.position = "top",
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank()) +
  scale_fill_discrete(labels =c("Compound / Overall", "Stand Alone")) +
  scale_y_continuous(expand = expansion(mult = c(.04, 0.02))) +
  guides(fill = guide_legend(reverse=TRUE))

ggsave(    
    filename = "ontario-plots/CT-sa-compounds-sum.pdf",
    width = 8,
    height = 10
    )


```


### Stand-alone content types per discipline


```{r CT-discipline-sa, fig.height=4, fig.width=8}

ggplot(df.sa.subject.sum, aes(x=reorder(Discipline, Total), y = Total)) +
    geom_bar(stat="identity", width = .7, fill= "#2fbfc4", colour = "#2fbfc4") +
    coord_flip() +
    my_theme +
    xlab("Discipline") +
    ylab("Number of Content Types in the Ontario Repository") +
    ggtitle("H5P Stand Alone Content Types by Discipline in the Ontario Repository") +
    geom_text(aes(label=Total), size=3, hjust=-0.3) +
    theme(plot.margin = margin(12,12,12,12)) +
    scale_x_discrete(expand = expansion(mult = c(0, 0))) +
    scale_y_continuous(expand = expansion(mult = c(0, .055)))

ggsave(    
    filename = "ontario-plots/CT-discipline-sa.pdf",
    width = 8,
    height = 4
    )

```


### Disciplines with more than 30 Stand Alone Content Types

The following data restricts the visualization only to disciplines with more then 30 stand alone content types. This reflects a limit of about 100 content types in total. (The only exception is Earth & Environment with 96 content types.)


### All content types per discipline, stacked horizontal as SA, QS, CP and IV

```{r CT-kind-30-disc-stack, fig.height=4, fig.width=8}

ggplot(df.disc.30.long, aes(x=reorder(Discipline, Overall), y=N, fill=CT.Kind)) +
  geom_bar(stat="identity", width = .8) +
  coord_flip() + 
  my_theme +
  labs(x = "Discipline", 
       y = "Number of Content Types",
       title = "Content Types in Different Enviroments in the Ontario Repository",
       fill = "Content Types"
       ) +
  theme(plot.margin = margin(12,12,12,12),
        legend.position = "top",
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank()) +
  scale_fill_discrete(labels =  c(
    "in Course Presentation", 
    "in Interactive Video",
    "in Question Set", 
    "Stand Alone")
    ) +
  guides(fill = guide_legend(reverse=TRUE)) +
  # geom_text(aes(label=N), size=2.5, hjust = 1, colour = "white") +
  geom_text(aes(y =label_y, label = N), size=3, check_overlap = TRUE) +
  geom_text(aes(y= Overall, label=Overall), size=3.5, hjust=-0.4) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.06))) # coord_flip() reverses axis

ggsave(    
    filename = "ontario-plots/CT-kind-30-disc-stack.pdf",
    width = 8,
    height = 4
    )

```

### All content types per discipline, stacked vertical as SA, QS, CP and IV (not displayed)

```{r CT-30-kind-disc-stack, fig.height=6, fig.width=8, eval=FALSE}


ggplot(df.disc.30.long, aes(x=Discipline, y=N, fill=CT.Kind)) +
  geom_bar(stat="identity", width = .8) +
  my_theme +
  labs(x = "Discipline", 
       y = "Number of Content Types",
       title = "Content Types in Different Enviroments in the Ontario Repository",
       fill = "Content Types"
       ) +
  theme(plot.margin = margin(12,12,12,12),
        axis.text.x = element_text(angle=50,hjust=1),
        legend.position = "top",
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank()) +
  scale_fill_discrete(labels =  c(
    "in Course Presentation", 
    "in Interactive Video",
    "in Question Set", 
    "Stand Alone")
    ) +
  guides(fill = guide_legend(reverse=TRUE)) +
#  geom_label(aes(y =label_y, label = N), size=3, label.size = 0.5, colour = "white") +
  geom_text(aes(y =label_y, label = N), size=3, check_overlap = TRUE) +
  geom_text(aes(y= Overall, label=Overall), size=3.5, vjust=-0.6) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.07))) 


ggsave(    
    filename = "ontario-plots/CT-30-kind-disc-stack.pdf",
    width = 8,
    height = 6
    )

```


### Kind of content types by discipline, dodged horizontal

```{r CT-30-kind-disc-dodge, fig.height = 10, fig.width=8}

ggplot(df.disc.30.long, aes(x=Discipline, y=N, fill=CT.Kind)) +
  geom_bar(stat="identity", position = "dodge") +
  coord_flip() + 
  my_theme +
  labs(x = "Discipline", 
       y = "Number of Content Types",
       title = "Different Categories of Content Types in the Ontario Repository",
       fill = "Content Types"
       ) +
  theme(plot.margin = margin(12,12,12,12),
        legend.position = "top",
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank()) +
  scale_fill_discrete(labels =  c(
    "in Course Presentation", 
    "in Interactive Video",
    "in Question Set", 
    "Stand Alone")
    ) +
#  geom_text(aes(label=N), size=2.5, vjust = -4, hjust = 1) +
  guides(fill = guide_legend(reverse=TRUE))  +
    scale_y_continuous(expand = expansion(mult = c(0, 0.07)))
#  scale_y_continuous(expand = expansion(mult = c(0, 0.05))) # coord_flip() reverses axis

ggsave(    
    filename = "ontario-plots/CT-30-kind-disc-dodge.pdf",
    width = 8,
    height = 10
    )

```


### Kind of content types by discipline, proportional stacked horizontal

```{r CT-30-kind-disc-prop, fig.height = 6, fig.width=8}

df.disc.30.prop <- df.disc.30.long %>% 
  group_by(Discipline) %>%
  mutate(prop = (N / sum(N) * 100)) %>% 
  mutate(label = cumsum(prop) - 0.5 * prop)
  

ggplot(df.disc.30.prop, aes(x=reorder(Discipline, Overall), y=prop, fill=CT.Kind)) +
  geom_bar(stat="identity", position = "stack", width = .8) +
  coord_flip() + 
  my_theme +
  labs(x = "Content Type", 
       y = "Percentage of Content Types",
       title = "Proportional Distribution of H5P Stand Alone Content Types, 
       Question Sets, Course Presentations and Interactive Videos
       in the Disciplines of the Ontario Repository",
       fill = "Content Types"
       ) +
#  geom_text(aes(y=label_y, label=Overall), size=2.5, hjust = 1) +
  theme(plot.margin = margin(12,12,12,12),
        legend.position = "top",
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank()) +
  scale_fill_discrete(labels =  c(
    "in Course Presentation", 
    "in Interactive Video",
    "in Question Set", 
    "Stand Alone")
    ) +
  geom_label(aes(y = label, label=sprintf("%.0f%%",prop)), size=4, label.size = 0.7, colour = "white") +
  guides(fill = guide_legend(reverse=TRUE))
#  scale_y_continuous(expand = expansion(mult = c(0, 0)))

ggsave(    
    filename = "ontario-plots/CT-30-kind-disc-prop.pdf",
    width = 8,
    height = 6
    )


```

### Number of content types per compounds QS, IV and CP

```{r compounds-by-subject, fig.height = 4, fig.width=8}

df.ct.in.compounds <- df.sa.subject %>% 
  filter(ContentType == "Question Set" |
         ContentType == "Interactive Video" |
         ContentType == "Course Presentation") %>% 
  bind_rows(df.QS.disc.total, df.CP.disc.total, df.IV.disc.total) %>% 
  pivot_longer(!ContentType, names_to = "Discipline", values_to = "N") %>%
  pivot_wider(names_from = ContentType, values_from = N) %>% 
  filter(`Question Set` > 1) %>% # (not: Arts, History, Law, Literature & Philosophy)
  mutate(QS.CT = QS.Total / `Question Set`) %>% 
  mutate(CP.CT = CP.Total / `Course Presentation`) %>% 
  mutate(IV.CT = IV.Total / `Interactive Video`) %>% 
  mutate(across(where(is.double), round, 1))

df.ct.in.compounds[2,1] <- "Computing"

df.ct.total.compounds <- adorn_totals(df.ct.in.compounds, "row")

#############################


  

# not necessary anymore as I have filtered those disciplines with division 0 = NaN
#  replace_na(list(QS.CT=0, CP.CT=0, IV.CT=0))  

# df.ct.in.compounds <- as.data.frame(t(df.ct.in.compounds)) %>% 
#   row_to_names(row_number = 1)

Compounds.Sum <- df.ct.in.compounds %>%
   summarise(across(where(is.numeric), sum))
# 
# CT.mean$Discipline <- "Means"
# 
# df.ct.in.compounds <-  add_row(df.ct.in.compounds, CT.mean)


##### Write table to hard disc and import it to TablePress for WordPress
# library(xlsx)
# write.table(df.ct.in.compounds, 
#             "ontario-tabs/cts-in-compounds.txt", sep=",")






```

```{r compounds-CTs-by-subject, fig.height = 4, fig.width=8, eval=FALSE}
library(RColorBrewer)
# display.brewer.all() # show all palettes

ggplot(df.ct.in.compounds, aes(y= `Question Set`, x= QS.Total, colour = Discipline)) +
  geom_point(size = 4) +
  theme(legend.position = "top") +
  scale_colour_brewer(palette = "Paired")
  
ggplot(df.ct.in.compounds, aes(y= `Course Presentation`, x= CP.Total, colour = Discipline)) +
  geom_point(size = 4) +
  theme(legend.position = "top") +
  scale_colour_brewer(palette = "Paired")

ggplot(df.ct.in.compounds, aes(y= `Interactive Video`, x= IV.Total, colour = Discipline)) +
  geom_point(size = 4) +
  theme(legend.position = "top") +
  scale_colour_brewer(palette = "Paired")
```


### Scatterplot with number CT in number of compounds and mean

```{r splot-compounds-CTs-avg-by-subject, fig.height = 5, fig.width=8}
library(RColorBrewer)
# display.brewer.all() # show all palettes

ggplot(df.ct.in.compounds, 
       aes(x = QS.CT, y = QS.Total, size = `Question Set`)) +
  geom_point(shape = 21, colour = "black", fill="Gold") +
  my_theme +
  labs(x = "Average Number of Content Types per Question Set", 
       y = "Number of Content Types in all Question Set per Discipline",
       title = "Total Number of Content Types in all Question Sets 
       and Average Number per one Question Set per Discipline"
       ) +
  theme(plot.margin = margin(12,12,12,12),
        axis.title.y = element_text(margin = margin(r = 10)),
        axis.title.x = element_text(margin = margin(t = 10)),
        legend.position = "top") +
  scale_y_continuous(breaks = seq(0, 400, by = 25),
      expand = expansion(mult = c(0.1, 0.1))) +
  scale_x_continuous(breaks = seq(4, 9, by = .25)) +
  scale_colour_brewer(palette = "Paired") +
  scale_size() +
  geom_text(aes(label=Discipline), size = 3, colour = "darkblue", vjust = -1.5) +
  geom_text(aes(label=`Question Set`), size = 3.5, colour = "darkred", vjust = 2.2)

ggsave(    
    filename = "ontario-plots/compounds-QS-avg-by-subject.pdf",
    width = 8,
    height = 6
    )

ggplot(df.ct.in.compounds, 
       aes(x = CP.CT, y = CP.Total, size = `Course Presentation`)) +
  geom_point(shape = 21, colour = "black", fill="Khaki") +
  my_theme +
  labs(x = "Average Number of Content Types per Course Presentation", 
       y = "Number of Content Types in all Course Presenetations per Discipline",
       title = "Total Number of Content Types in all Course Presentations 
       and Average Number per one Course Presentation per Discipline"
       ) +
  theme(plot.margin = margin(12,12,12,12),
        axis.title.y = element_text(margin = margin(r = 10)),
        axis.title.x = element_text(margin = margin(t = 10)),
        legend.position = "top") +
  scale_y_continuous(breaks = seq(0, 160, by = 20),
                     expand = expansion(mult = c(0.1, 0.1))) +
  scale_x_continuous(breaks = seq(0, 5, by = .25)) +
  scale_colour_brewer(palette = "Paired") +
  scale_size() +
  geom_text(aes(label=Discipline), size = 3, colour = "darkblue", vjust = -1.5) +
  geom_text(aes(label=`Course Presentation`), size = 3.5, colour = "darkred", vjust = 2.2)

ggsave(    
    filename = "ontario-plots/compounds-CP-avg-by-subject.pdf",
    width = 8,
    height = 6
    )

ggplot(df.ct.in.compounds, 
       aes(x = IV.CT, y = IV.Total, size = `Interactive Video`)) +
  geom_point(shape = 21, colour = "black", fill="cornsilk") +
  my_theme +
  labs(x = "Average Number of Content Types per Interactive Video", 
       y = "Number of Content Types in all Interactive Videos per Discipline",
       title = "Total Number of Content Types in all Interactive Videos 
       and Average Number per one Interactive Video per Discipline"
       ) +
  theme(plot.margin = margin(12,12,12,12),
        axis.title.y = element_text(margin = margin(r = 10)),
        axis.title.x = element_text(margin = margin(t = 10)),
        legend.position = "top") +
  coord_cartesian(ylim = c(0,100)) +
  scale_x_continuous(breaks = seq(0, 5, by = .25)) +
  scale_colour_brewer(palette = "Paired") +
  scale_size() +
  geom_text(aes(label=Discipline), size = 3, colour = "darkblue", vjust = -1.5) +
  geom_text(aes(label=`Interactive Video`), size = 3.5, colour = "darkred", vjust = 2.2)

ggsave(    
    filename = "ontario-plots/compounds-IV-avg-by-subject.pdf",
    width = 8,
    height = 6
    )


```
